---
title: "development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(googlesheets4)
library(lubridate)
library(janitor)
library(plotly)
```

# Ideas
How do I want to serve up results?
1) Shiny App
2) Flexdashboard - can this be embedeed as a blog post?
3) Interactive plots in a Blog post

Likely path is to create a flexdashboard for my blog, then have a blogpost with a link to the flexdashboard.
The flexdashboard itself will not be in the blog post.

https://blogdown-demo.rbind.io/2017/09/06/adding-r-markdown-documents-of-other-output-formats/
https://github.com/yihui/blogdown-static


https://community.rstudio.com/t/host-flexdashboard-on-blogdown-site/76355



This seems to have a flexdashboard in the blogpost
https://www.benjaminsorensen.me/post/libib-dashboard/

# Connect to google sheets
Browser authentication and store credentials to be used  between R sessions locally
```{r}
run_df <- read_sheet("https://docs.google.com/spreadsheets/d/16rDndbsyUb95yq5CbrtPGWWWnP0FB_HoMU2YUdj2y2s",
                     col_types = "Ddddd") %>% 
  clean_names() %>% 
  fill(date)

```

remove the data that did not record 1 km spilts (just one entry for entire run)
then for each split, calculate the time for that distance
```{r}
run_df1 <- run_df %>% 
  filter(split_distance <= 1) %>% 
  mutate(split_pace_minutes2 = split_pace_minutes + split_pace_seconds/60,
         split_minutes = split_distance * split_pace_minutes2) %>% 
  mutate(temp = case_when(nchar(split_pace_seconds) == 1 ~ paste0("0",split_pace_seconds),
                          TRUE ~ as.character(split_pace_seconds)
                          )
         ) %>% 
  unite(split_pace_ms_chr, split_pace_minutes, temp, sep = ":") %>% 
  select(-split_pace_minutes2, -split_pace_seconds)
```



# calculations

group the splits and do summary calculations  
```{r}
run_collatedruns_df1 <- run_df1 %>% 
  group_by(date, run) %>% 
  summarise(run_distance = sum(split_distance), run_minutes = sum(split_minutes)) %>% 
  mutate(avg_pace = run_minutes / run_distance,
         avg_pace_minutes = trunc(avg_pace),
         avg_pace_seconds = round((avg_pace - avg_pace_minutes)*60, digits = 0)) %>% 
  mutate(temp = case_when(nchar(avg_pace_seconds) == 1 ~ paste0("0",avg_pace_seconds),
                          TRUE ~ as.character(avg_pace_seconds)
                          )
         ) %>%
  mutate(avg_pace_chr = paste0(avg_pace_minutes,"'", temp, "\"/km")) %>% 
  # unite(avg_pace_chr2, avg_pace_minutes, temp, sep = ":") %>% 
  select(-avg_pace_minutes, -temp, -avg_pace_seconds,)


```




```{r}
run_df2 <- run_df %>% 
  filter(split_distance > 1) %>% 
  mutate(run_distance = split_distance,
         run_minutes = split_pace_minutes + split_pace_seconds / 60) %>% 
  mutate(avg_pace = run_minutes / run_distance,
         avg_pace_minutes = trunc(avg_pace),
         avg_pace_seconds = round((avg_pace - avg_pace_minutes)*60, digits = 0)) %>% 
  mutate(temp = case_when(nchar(avg_pace_seconds) == 1 ~ paste0("0",avg_pace_seconds),
                          TRUE ~ as.character(avg_pace_seconds)
                          )
         ) %>%
  mutate(avg_pace_chr = paste0(avg_pace_minutes,"'", temp, "\"/km")) %>% 
  # unite(avg_pace_chr2, avg_pace_minutes, temp, sep = ":") %>% 
  select(-avg_pace_minutes, -temp, -avg_pace_seconds, -split_distance, -split_pace_minutes, -split_pace_seconds)

```


Apply some filters - maybe these can be dynamic filter with presets
```{r}
run_df3 <- run_collatedruns_df1 %>% 
  bind_rows(run_df2) %>% 
  mutate(year = year(date)) %>% 
  filter(avg_pace < 9) %>%  # any runs greater than 9min/km was either walking, or part of the run was walking or complete stand still to catch pokemon or hack a portal
  filter(run_distance > 3) %>% 
  arrange(date) %>% 
  # make the date as day month and add factor levels based on the dataframe order
  mutate(datemd = paste(day(date), month(date, label = TRUE, abbr = TRUE), sep="-"),
         datemd = factor(datemd, levels = unique(datemd)))
  
```



# visualisations

number of runs per year

```{r}

run_df3 %>% 
  group_by(year) %>% 
  summarise(num_runs = n()) %>% 
  ggplot(aes(x = factor(year), y = num_runs)) +
  geom_col(fill = "darkred") +
  geom_text(aes(label =  num_runs, y= num_runs), vjust = -0.5, colour = "black") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) +
  labs(x = "Year", y = "Number of runs") 

```


pace by date / run

Turn your 'treatment' column into a character vector
data$Treatment <- as.character(data$Treatment)
Then turn it back into a factor with the levels in the correct order
data$Treatment <- factor(data$Treatment, levels=unique(data$Treatment))

```{r}
p1 <- run_df3 %>% 
  filter(year == 2016) %>% 
  ggplot() +
  geom_point(aes(x=datemd, 
                 y = avg_pace, 
                 colour = run_distance, 
                 text = paste("Date:", datemd, 
                              "\nPace:", avg_pace_chr,
                              "\nDistance", run_distance, "km")
                          
                 )
             ) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) 

ggplotly(p1, tooltip = "text")
```


```{r}
run_df3 %>% 
  ggplot() +
  geom_point(aes(x=datemd, 
                 y = avg_pace, 
                 colour = run_distance, 
                 text = paste("Date:", datemd, 
                              "\nPace:", avg_pace_chr,
                              "\nDistance", run_distance, "km")
                          
                 )
             ) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, vjust = 0.5))  +
  facet_wrap(~year)
```

