---
title: "development"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(googlesheets4)
```

# Ideas
How do I want to serve up results?
1) Shiny App
2) Flexdashboard - can this be embedeed as a blog post?
3) Interactive plots in a Blog post

Likely path is to create a flexdashboard for my blog, then have a blogpost with a link to the flexdashboard.
The flexdashboard itself will not be in the blog post.

https://blogdown-demo.rbind.io/2017/09/06/adding-r-markdown-documents-of-other-output-formats/
https://github.com/yihui/blogdown-static


https://community.rstudio.com/t/host-flexdashboard-on-blogdown-site/76355



This seems to have a flexdashboard in the blogpost
https://www.benjaminsorensen.me/post/libib-dashboard/

# Connect to google sheets
Browser authentication and store credentials to be used  between R sessions locally
```{r}
run_df <- read_sheet("https://docs.google.com/spreadsheets/d/16rDndbsyUb95yq5CbrtPGWWWnP0FB_HoMU2YUdj2y2s")

```


```{r}

```

